---
title: "Job Explorer"
editor_options: 
  chunk_output_type: console
format:
  html:
    toc: false
---

```{r}
library(dplyr)
for (i in list.files(here::here("R"), full.names = TRUE)) source(i)

googlesheets4::gs4_deauth()

link <- "https://docs.google.com/spreadsheets/u/0/d/1P7BfU0emdcGFVIWIs_erFxyy0UGXXORw7h0rpU19gQ8/htmlview#gid=1219796980"

today <- Sys.Date()
dttm <- pretty_datetime(Sys.time())
```

Last updated on `r dttm`

> Displaying the information related to Ecology and Evolutionary Biology Jobs 
posted and maintained on [__ecoevojobs.net__ googlesheet](`r link`).

```{r}
faculty_permanent <- googlesheets4::read_sheet(
  link,
  sheet = 1,
  skip = 1
) |>
  janitor::clean_names() |>
  mutate(
    across(
      c(timestamp, review_date, last_update),
      ~ lubridate::as_date(.x)
    )
  ) |>
  rename(
    notes = notes_10
  ) |> 
  select(
    timestamp:notes
  ) |> 
  mutate(
    notes = purrr::map(notes, as.character)
  ) |> 
  tidyr::unnest(
    cols = notes,
    keep_empty = TRUE
  ) |> 
  arrange(
    desc(timestamp)
  )

postdoc <- googlesheets4::read_sheet(
  link,
  sheet = 2,
  skip = 1
) |>
  janitor::clean_names() |>
  mutate(
    across(
      c(timestamp, review_date, last_update),
      ~ lubridate::as_date(.x)
    )
  ) |>
  select(
    timestamp:notes
  ) |>
  mutate(
    notes = purrr::map(notes, as.character)
  ) |> 
  tidyr::unnest(
    cols = notes,
    keep_empty = TRUE
  ) |> 
  arrange(
    desc(timestamp)
  )
```

::: {.callout-tip}
# Jobs added today

### Faculty / Permanent jobs

```{r}
faculty_permanent |> 
  filter(
    timestamp > today - 1
  ) |> 
  select(
    location,
    institution,
    position_type,
    rank,
    subject_area
  ) |> 
  reactable::reactable()
```

### Postdoc jobs 

```{r}
postdoc |> 
  filter(
    timestamp > today - 1
  ) |> 
  select(
    location,
    institution,
    subject_area,
    pi
  ) |> 
  reactable::reactable()
```

See complete list and urls below.
:::

# Faculty / Permanent Jobs

> **You can interact with the table** \
>   - **Group by**: select the variable you want to group by \
>   - **Filter**: search for a value in the boxes under the column name \
>   - **Search**: search entire table using the `Search` box in top-right \
>   - **Sort columns**: click the name of the column \
>   - **Resize columns**: pull the column borders to resize column width \
>   - **Expand**: Click the expand button to see notes from community \


```{r}
library(htmltools)

htmltools::browsable(
  tagList(
    div(tags$label("Group by", `for` = "faculty-grouping-select")),
    tags$select(
      id = "faculty-grouping-select",
      onchange = "Reactable.setGroupBy('faculty-grouping-table', this.value ? [this.value] : [])",
      tags$option("None", value = ""),
      lapply(
        c("location", "institution", "position_type", "rank", "subject_area"), 
        tags$option
      )
    ),

    tags$hr("aria-hidden" = "true"),

    faculty_permanent |>
      select(
        location,
        institution,
        timestamp,
        position_type,
        rank,
        subject_area,
        review_date,
        url
      ) |> 
      filter(
        !if_any(
          everything(),
          ~ is.na(.x) | trimws(.x) == ""
        )
      ) |>
      reactable::reactable(
        style = list(fontFamily = "Work Sans, sans-serif", fontSize = "14px"),
        sortable = TRUE,
        resizable = TRUE,
        filterable = TRUE,
        searchable = TRUE,
        columns = list(
          url = reactable::colDef(
            cell = function(value) {
              htmltools::tags$a(
                href = value, target = "_blank", rel = "noopener noreferrer", value
              )
            },
            minWidth = 60,
            sortable = FALSE,
            filterable = FALSE
          ),
          institution = reactable::colDef(minWidth = 180),
          timestamp = reactable::colDef(minWidth = 80),
          review_date = reactable::colDef(minWidth = 80),
          subject_area = reactable::colDef(minWidth = 160),
          location = reactable::colDef(minWidth = 150),
          rank = reactable::colDef(minWidth = 140)
        ),
        rowStyle = function(index) {
          list(height = "100px", whiteSpace = "normal") # Sets height to 50px for all rows
        },
        details = function(index) {
          htmltools::div(
            style = "padding: 10px;",
            htmltools::tagList(
              "More info: ",
              htmltools::tags$br(),
              htmltools::tags$br(),
              "[Last updated on]",
              htmltools::tags$br(),
              if_else(
                is.na(faculty_permanent$last_update[index]),
                "not available",
                as.character(faculty_permanent$last_update[index])
              ),
              htmltools::tags$br(),
              htmltools::tags$br(),
              "[Notes]",
              htmltools::tags$br(),
              if_else(
                is.na(faculty_permanent$notes[index]),
                "not available",
                faculty_permanent$notes[index]
              )
            )
          )
        },
        striped = TRUE,
        highlight = TRUE,
        bordered = TRUE,
        showPageSizeOptions = TRUE,
        theme = reactable::reactableTheme(
          borderColor = "#dfe2e5",
          stripedColor = "#f6f8fa",
          highlightColor = "#FDBF6F",
          cellPadding = "8px 12px"
        ),
        defaultPageSize = 10,
        elementId = "faculty-grouping-table"
      )
  )
)
```

# Postdoc Jobs

```{r}

htmltools::browsable(
  tagList(
    div(tags$label("Group by", `for` = "postdoc-grouping-select")),
    tags$select(
      id = "postdoc-grouping-select",
      onchange = "Reactable.setGroupBy('postdoc-grouping-table', this.value ? [this.value] : [])",
      tags$option("None", value = ""),
      lapply(
        c("location", "institution", "subject_area", "pi"), 
        tags$option
      )
    ),

    tags$hr("aria-hidden" = "true"),
    
    
    postdoc |>
      select(
        - notes,
        - last_update
      ) |>
      filter(
        !if_any(
          everything(),
          ~ is.na(.x) | trimws(.x) == ""
        )
      ) |>
      reactable::reactable(
        style = list(fontFamily = "Work Sans, sans-serif", fontSize = "14px"),
        sortable = TRUE,
        resizable = TRUE,
        filterable = TRUE,
        searchable = TRUE,
        columns = list(
          url = reactable::colDef(
            cell = function(value) {
              htmltools::tags$a(
                href = value, target = "_blank", rel = "noopener noreferrer", value
              )
            },
            minWidth = 60,
            sortable = FALSE,
            filterable = FALSE
          ),
          institution = reactable::colDef(minWidth = 200),
          timestamp = reactable::colDef(minWidth = 80),
          review_date = reactable::colDef(minWidth = 80),
          subject_area = reactable::colDef(minWidth = 160),
          location = reactable::colDef(minWidth = 140),
          pi = reactable::colDef(minWidth = 140)
        ),
        rowStyle = function(index) {
          list(height = "100px", whiteSpace = "normal") # Sets height to 50px for all rows
        },
        details = function(index) {
          htmltools::div(
            style = "padding: 10px;",
            htmltools::tagList(
              "More info: ",
              htmltools::tags$br(),
              htmltools::tags$br(),
              "[Last updated on]",
              htmltools::tags$br(),
              if_else(
                is.na(postdoc$last_update[index]),
                "not available",
                as.character(postdoc$last_update[index])
              ),
              htmltools::tags$br(),
              htmltools::tags$br(),
              "[Notes]",
              htmltools::tags$br(),
              if_else(
                is.na(postdoc$notes[index]),
                "not available",
                postdoc$notes[index]
              )
            )
          )
        },
        striped = TRUE,
        highlight = TRUE,
        bordered = TRUE,
        showPageSizeOptions = TRUE,
        theme = reactable::reactableTheme(
          borderColor = "#dfe2e5",
          stripedColor = "#f6f8fa",
          highlightColor = "#FDBF6F",
          cellPadding = "8px 12px"
        ),
        defaultPageSize = 10,
        elementId = "postdoc-grouping-table"
      )
  )
)
```

